---
output: github_document
editor_options: 
  chunk_output_type: console
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

version <- as.vector(read.dcf('DESCRIPTION')[, 'Version'])
version <- gsub('-', '.', version)  
```

# strayr
<!-- badges: start -->
[![Build Status](https://travis-ci.org/MattCowgill/strayr.svg?branch=master)](https://travis-ci.org/MattCowgill/strayr)
[![codecov status](https://img.shields.io/codecov/c/github/mattcowgill/strayr.svg)](https://codecov.io/gh/MattCowgill/strayr)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

<!-- badges: end -->

## Overview
strayr is a simple tool to wrangle messy Australian state names and/or abbreviations
into a consistent format.

## Installation

Install from GitHub with:
```{r gh-installation, eval = FALSE}
# if you don't have devtools installed, first run:
# install.packages("devtools")
devtools::install_github("mattcowgill/strayr")
```


## Examples

Let's start with a character vector that includes some misspelled State names,
some correctly spelled state names, as well as some abbreviations both malformed
and correctly formed.

```{r create-string}

x <- c("western Straya", "w. A ", "new soth wailes", "SA", "tazz", "Victoria",
       "northn territy")

```

To convert this character vector to a vector of abbreviations for State names,
simply use the `strayr()` function:

```{r strayr1}
library(strayr)
strayr(x)

```

If you want full names for the states rather than abbreviations:

```{r strayr-fullnames}

strayr(x, to = "state_name")

```

By default, `strayr()` uses fuzzy or approximate string matching to match the 
elements in your character vector to state names/abbreviations. If you only want
to permit exact matching, you can disable fuzzy matching. This means you will 
never get false matches, but you will also fail to match misspelled state names 
or malformed abbreviations; you'll get an `NA` if no match can be found.

```{r strayr-exact}
 strayr(x, fuzzy_match = FALSE)

```

If your data is in a data frame, `strayr()` works well within a `dplyr::mutate()` call:

```{r dplyr}

 x_df <- data.frame(state = x, stringsAsFactors = FALSE)

library(dplyr)
 x_df %>% 
   mutate(state_abbr = strayr(state))
```

### Australian Public Holidays
This package includes the `auholidays` dataset from the [Australian Public Holidays Dates Machine Readable Dataset](https://data.gov.au/data/dataset/australian-holidays-machine-readable-dataset) as well as a helper function `is_holiday`:

```{r is_holiday_example}
str(auholidays)


is_holiday('2020-01-01')
is_holiday('2019-05-27', jurisdictions=c('ACT', 'TAS'))

h_df <- data.frame(dates = c('2020-01-01', '2020-01-10'))

h_df %>%
  mutate(IsHoliday = is_holiday(dates))
```
